---
title: "p8105_hw6_ncl2127"
output: github_document
date: "2023-11-27"
---

```{r}
library(tidyverse)
library(tidyr)
library(dplyr)
library(stringr)
library(ggplot2)
library(broom)
library(purrr)
library(modelr)
library(mgcv)

```

Problem 2

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2022-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```

```{r}
boot_straps = 
  weather_df |>
  modelr::bootstrap(n = 5000)|>
  pull(strap) |>
  nth(1) |>
  as_tibble()
  
boot_strap_res = weather_df |>
  modelr::bootstrap(n = 5000) |>
  mutate(
    models = map(strap, \(df) lm(tmax ~ tmin + prcp, data = df) ),
    results = map(models, broom::tidy),
    glance = map(models, broom::glance)) |> 
  select(-strap, -models) |>
  unnest(results)|>
  janitor::clean_names()

```

```{r}

tmin_boot = boot_strap_res |> filter(term == "tmin")
prcp_boot = boot_strap_res |> filter(term == "prcp")

boot_strap_log = log(tmin_boot$estimate*prcp_boot$estimate)|> as_tibble()|> rowid_to_column(var = "id") |> drop_na() |> rename(logB1_B2 = value)

r_squared_boot = boot_strap_res |> select(id, glance) |> unnest(glance)|>janitor::clean_names()|> distinct(id, .keep_all = TRUE)

log_plot = ggplot(boot_strap_log, aes(x = logB1_B2)) +
  geom_density()

r_sq_plot = ggplot(r_squared_boot, aes(x = r_squared)) + 
  geom_density()

log_plot

r_sq_plot

conf_int_log <- boot_strap_log |>
  summarize(
    ci_lower = quantile(logB1_B2, 0.025), 
    ci_upper = quantile(logB1_B2, 0.975))

conf_int_rsq <- r_squared_boot |>
  summarize(
    ci_lower = quantile(r_squared, 0.025), 
    ci_upper = quantile(r_squared, 0.975))
 
```
The $log(\beta_{1}*\beta_{2})$ plot shows a moderately left-skewed distribution. The r-squared plot shows a relatively left-skewed distribution as well, however it seems to be less skewed than the log plot. Both distributions follow a normal distribution somewhat closely, but not exactly due to their skewness. We are 95% confident that the true $log(\beta_{1}*\beta_{2})$ value lies between the interval of (`r conf_int_log$ci_lower`, `r conf_int_log$ci_upper`). We are 95% confident that the true r-squared value lies between the interval of (`r conf_int_rsq$ci_lower`, `r conf_int_rsq$ci_upper`).

Problem 3

## Dataset cleaning
```{r}
bw_df = read_csv("data/birthweight.csv") |>
  drop_na()

bw_df$babysex <- factor(bw_df$babysex, levels = c("1", "2"))
bw_df$frace <- factor(bw_df$frace, levels = c("1", "2", "3", "4", "8", "9"))
bw_df$malform <- factor(bw_df$malform, levels = c("0", "1"))
bw_df$mrace <- factor(bw_df$mrace, levels = c("1", "2", "3", "4", "8"))

bw_df <- bw_df |> mutate(babysex = fct_recode(babysex, male = "1", female = "2")) |> mutate(frace = fct_recode(frace, white = "1", black = "2", asian = "3", puerto_rican = "4", other = "8", unknown = "9")) |>
  mutate(malform = fct_recode(malform, absent = "0", present = "1")) |>
  mutate(mrace = fct_recode(mrace, white = "1", black = "2", asian = "3", puerto_rican = "4", other = "8"))

```

## Regression model
```{r}
bw_df |> ggplot(aes(x = bhead, y = bwt)) + geom_point()
bw_df |> ggplot(aes(x = blength, y = bwt)) + geom_point()
bw_df |> ggplot(aes(x = gaweeks, y = bwt)) + geom_point()

my_model_1 = lm(bwt ~ gaweeks + delwt + bhead, data = bw_df)

gaweeks_resid = bw_df |>
  modelr::add_residuals(my_model_1) |>
  ggplot(aes(x = gaweeks, y = resid)) +geom_point()

delwt_resid = bw_df |>
  modelr::add_residuals(my_model_1) |>
  ggplot(aes(x = delwt, y = resid)) +geom_point()

bhead_resid = bw_df |>
  modelr::add_residuals(my_model_1) |>
  ggplot(aes(x = bhead, y = resid)) + geom_point()

gaweeks_resid
delwt_resid
bhead_resid

gaweeks_predict = bw_df |>
  modelr::add_predictions(my_model_1) |>
  ggplot(aes(x = gaweeks, y = pred)) + geom_point()

delwt_predict = bw_df |>
  modelr::add_predictions(my_model_1) |>
  ggplot(aes(x = delwt, y = pred)) + geom_point()

bhead_predict = bw_df |>
  modelr::add_predictions(my_model_1) |>
  ggplot(aes(x = bhead, y = pred)) + geom_point()

bhead_predict
delwt_predict
gaweeks_predict
```

I created this model based on a hypothesized structure for the factors underlying birthweight by viewing the plotted relationship between each factor and birthweight. I noticed that gestational age, head circumference at birth, and length at birth were seemed to have a stronger positive_____ correlation with birthweight. I additionally chose mother's weight at delivery as a third and final variable  in my MLR model due to the genetic component involved in determining the baby's birth weight (which of course is impacted by the father's weight as well, however in this case we are only provided the mother's delivery weight information).


```{r}
blength_gaweeks = lm(bwt ~ gaweeks + blength, data = bw_df)

bhead_blength_ga = lm(bwt ~ gaweeks*blength + blength*bhead + gaweeks*bhead + gaweeks*blength*bhead, data = bw_df)

cv_df =
  crossv_mc(bw_df, nrow(bw_df))

cv_df =
  cv_df |> 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
  
cv_df = 
  cv_df |> 
  mutate(
    my_model_1  = map(train, \(df) lm(bwt ~ gaweeks + delwt + bhead, data = df)),
    blength_gaweeks  = map(train, \(df) lm(bwt ~ gaweeks + blength, data = df)),
    bhead_blength_ga  = map(train, \(df) lm(bwt ~ gaweeks*blength + blength*bhead + gaweeks*bhead + gaweeks*blength*bhead, data = df))) |> 
  mutate(
    rmse_my_model_1 = map2_dbl(my_model_1, test, \(mod, df) rmse(model = mod, data = df)),
    rmse_blength_gaweeks = map2_dbl(blength_gaweeks, test, \(mod, df) rmse(model = mod, data = df)),
    rmse_bhead_blength_ga = map2_dbl(bhead_blength_ga, test, \(mod, df) rmse(model = mod, data = df)))

cv_df |> 
  select(starts_with("rmse")) |> 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") |> 
  mutate(model = fct_inorder(model)) |> 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```
Based on the cross-validation plot, it seems that the given model using the length at birth and gestation age and the given model using head circumference, length at birth, and gestational age had a wider, slightly reduced and significantly lower RMSEs, respectively, compared to the hypothesized model I created using gestational age, head circumference, and mother's weight at delivery. The head circumference, length at birth, and gestational age model is likely the best model of the three to predict birthweight.
